`SCPCL000824` - Validation of tumor cells

### 2024-06-18 analyses/cell-type-ewings/cell_type_annotations/SCPCS000492/SCPCL000824_tumor-cell-validation.Rmd
rendered notebook

# include both infercnv and copykat annotations in the cnv heatmap 
annotation <- ComplexHeatmap::rowAnnotation(infercnv = annotation_df$cnv_proportion_classification,
                                            copykat = annotation_df$copykat_classification,
                                            col = list(infercnv = c("Tumor" = "#00274C", "Normal" = "#FFCB05", "Ambiguous" = "grey"),
                                                       copykat = c("Tumor" = "#00274C", "Normal" = "#FFCB05", "Ambiguous" = "grey")))

>>>>

# include both infercnv and copykat annotations in the cnv heatmap 
annotation <- ComplexHeatmap::rowAnnotation(infercnv = annotation_df$cnv_proportion_classification,
                                            copykat = annotation_df$copykat_classification,
                                            col = list(infercnv = c("Tumor" = "#00274C", "Normal" = "#FFCB05", "Reference" = "grey"),
                                                       copykat = c("Tumor" = "#00274C", "Normal" = "#FFCB05")))
